Automatic Hadith Graphs using Arabic Morphological Analysis

### 2011-06-02 tex/hadith.ijcnlp.tex
merged and added small part to results section

\begin{table}[bt]
\centering
\caption{Results of the hadith case study with Sarf.}
%\begin{tabular}{|p{1.5cm}||c|c||c|c||c|c|} \hline
\resizebox{1.1\columnwidth}{!}{
\begin{tabular}{lcp{.2cm}cp{.2cm}c} %\cline{2-10}
 &  AlKafi & & AlIstibsar & &IbnHanbal \\ \cline{1-6}
Word count  &98,943 & & 103,835 & & 20,354 \\ 
 Names       & 12,060  & & 14,613& & 3,013\\
%Names/Narrator & 1.97 & & 1.84& & 1.25 \\
Narrators  & 2,623 & & 5,767& & 1,755 \\ 
%Narrators/Chain  & 4.84 & & 4.76 & &4.05 \\
Chains  & 542 &  & 1,211& & 433 \\ 
Ignored names  & 6,400 &  & 3,348 & & 642 \\ \hline
Segmentation accuracy  & 96\%& & 96\%& & 92\%\\ 
Chain accuracy & 99\%&  & 99\%& & 97\% \\ 
%Narrator accuracy  & & & & &  & & & \\ 
Narrator accuracy  & 91\%& & 90\% & & 90\% \\ \hline
%Name false positives  & 7\%&  & 4\% & & 4\% \\ \hline
Running time (secs.)& 1.32 & & 1.31 & & .096\\ \hline 
\end{tabular}
}
\normalsize
\label{t:hadithresallresults}
\end{table}

>>>>

%\begin{table}[bt]
%\centering
%\caption{Results of the hadith case study with Sarf.}
%%\begin{tabular}{|p{1.5cm}||c|c||c|c||c|c|} \hline
%\resizebox{1.1\columnwidth}{!}{
%\begin{tabular}{lcp{.2cm}cp{.2cm}c} %\cline{2-10}
% &  AlKafi & & AlIstibsar & &IbnHanbal \\ \cline{1-6}
%Word count  &98,943 & & 103,835 & & 20,354 \\ 
% Names       & 12,060  & & 14,613& & 3,013\\
%%Names/Narrator & 1.97 & & 1.84& & 1.25 \\
%Narrators  & 2,623 & & 5,767& & 1,755 \\ 
%%Narrators/Chain  & 4.84 & & 4.76 & &4.05 \\
%Chains  & 542 &  & 1,211& & 433 \\ 
%Ignored names  & 6,400 &  & 3,348 & & 642 \\ \hline
%Segmentation accuracy  & 96\%& & 96\%& & 92\%\\ 
%Chain accuracy & 99\%&  & 99\%& & 97\% \\ 
%%Narrator accuracy  & & & & &  & & & \\ 
%Narrator accuracy  & 91\%& & 90\% & & 90\% \\ \hline
%%Name false positives  & 7\%&  & 4\% & & 4\% \\ \hline
%Running time (secs.)& 1.32 & & 1.31 & & .096\\ \hline 
%\end{tabular}
%}
%\normalsize
%\label{t:hadithresallresults}
%\end{table}
%

\begin{table*}[bt]                                     
\centering                                            
\caption{Results comparing between NaGEMA and iTree.}
\resizebox{2.1\columnwidth}{!}{
\begin{tabular}{p{2.1cm}lp{.1cm}cccp{.1cm}cccp{.1cm}ccc}
%\multicolumn{13}{c}{NaGEMA with all refinements} \\ \cline{3-13}
& & & \multicolumn{3}{c}{segmentation} & &  \multicolumn{3}{c}{sanad boundary}  & &  \multicolumn{3}{c}{name boundary} \\
& & & recall & precision & F-score & & recall & precision & F-score & & recall & precision & F-score \\ \cline{2-14}
\multirow{3}{*}{NaGEMA }&musnad & & 1.000 & 1.000 & 1.000 & & 0.993 & 0.990 & 0.991 & & 0.999 & 0.998 & 0.999 \\
&kafi & & 1.000 & 0.920 & 0.958 & & 0.937 & 0.970 & 0.953 & & 0.993 & 0.988 & 0.990 \\
&istibsar & & 1.000 & 0.973 & 0.986 & & 0.980 & 0.950 & 0.965 & & 0.996 & 0.998 & 0.997 \\ \cline{2-14}
& & & 1.000 & 0.964 & 0.982 & & 0.970 & 0.970 & 0.970 & & 0.996 & 0.995 & 0.995 \\ \hline \hline
%& & &  &  &  & &  &  &  & &  &  & \\
%&\multicolumn{13}{c}{iTree} \\ \cline{3-13}
& & & \multicolumn{3}{c}{accept as hadith} & &  \multicolumn{3}{c}{sanad boundary}  & &  \multicolumn{3}{c}{name boundary} \\
& & & recall & precision & F-score & & recall & precision & F-score & & recall & precision & F-score \\ \cline{2-14}
\multirow{3}{*}{iTree} &musnad & & 1.000 & NA & 1.000 & & 0.997 & 0.977 & 0.987 & & 0.998 & 1.000 & 0.999  \\
&kafi & & 0.043 & NA & 0.083 & & 1.000 & 0.313 & 0.476 & & 1.000 & 1.000 & 1.000 \\
&istibsar & & 0.028 & NA & 0.054 & & 0.875 & 0.583 & 0.700 & & 1.000 & 1.000 & 1.000 \\ \cline{2-14}
& & & 0.357 & NA & 0.379 & & 0.957 & 0.624 & 0.721 & & 0.999 & 1.000 & 1.000 \\ 
 \end{tabular}                 
}                             
\normalsize                   
\label{t:hadithresults} 
\end{table*}

To evaluate our approach, we performed experiments on three books of 
hadith~\cite{IbnHanbal,AlTousi,AlKulayni} whose accuracy results are detailed in 
Tables~\ref{t:hadithresults} and \ref{t:nopunctlearnresults}. We used recall and precision as our evaluation metrics.
We report results on three levels of accuracy: segmentation, sanad boundary and
narrator boundary. Segmentation accuracy refers to the success of NaGEMA in
detecting in the plain text of a hadith book the locations of the different
narrations that it contains. While the sanad boundary is a measure of the accuracy
in reporting the correct number of narrators in the sanad. Finally, the narrator boundary refers
to the accuracy in reporting the correct number of words inside each narrator.

Precisely defined, segmentation recall refers to the fraction of extracted narrations from 
those which are correct; and segmentation precision refers to the fraction of correct narrations
from those extracted. Similarly, sanad boundary recall is a measure whether we detected all narrators
in the sand; and precision is a measure whether we did so without introducing much false positives.

iTree does not tackle the problem hadith segmentation. In contrast to NaGEMA, it does not work on a book level, 
instead it assumes that the knowledge of what part of the text of a hadith book is a narration is available.
Consequently, for the narrators to be extracted, the hadith must be manually extracted
from the book and inputted on its own to the tool. Still however, in many cases it does not recognize the structure of
the inputted hadith and is incapable of extracting any useful information from the narration. 
In table~\ref{t:hadithresults}, we report the fraction of narrations which iTree recognizes from those inputted, instead
of the segmentation measure used for NaGEMA. This measure is equivalent to the concept of recall; nonetheless, precision
in this context is not applicable since by default the input is required to be represent correctly extracted narrations.

Now we move to explain the significance of the experiments performed.

\begin{table*}[bt]                                     
\centering                                            
\caption{Results without punctuation and without learning. }
\resizebox{2.1\columnwidth}{!}{
\begin{tabular}{p{2.1cm}lp{.1cm}cccp{.1cm}cccp{.1cm}ccc}
& & & \multicolumn{3}{c}{segmentation} & &  \multicolumn{3}{c}{sanad boundary}  & &  \multicolumn{3}{c}{name boundary} \\
& & & recall & precision & F-score & & recall & precision & F-score & & recall & precision & F-score \\ \cline{2-14}
\multirow{3}{*}{no punctuation} 
& musnad  & & 1.000 & 1.000 & 1.000 & & 0.982 & 0.955 & 0.968 & & 1.000 & 0.998 & 0.999 \\ 
& kafi & & 1.000 & 0.793 & 0.885 & & 0.944 & 0.967 & 0.955 & & 0.996 & 0.938 & 0.966 \\
& istibsar & & 1.000 & 1.000 & 1.000 & & 0.980 & 0.931 & 0.955 & & 0.994 & 0.985 & 0.990 \\  \cline{2-14}
& &  & 1.000 & 0.931 & 0.962 & & 0.969 & 0.951 & 0.960 & & 0.997 & 0.974 & 0.985 \\ \hline \hline
%& & & \multicolumn{3}{c}{segmentation} & &  \multicolumn{3}{c}{sanad boundary}  & &  \multicolumn{3}{c}{name boundary} \\
%& & & recall & precision & F-score & & recall & precision & F-score & & recall & precision & F-score \\ \cline{2-14}
\multirow{3}{*}{no learning}
& musnad & & 1.000 & 1.000 & 1.000 & & 0.894 & 0.985 & 0.937 & & 0.995 & 1.000 & 0.998\\
& kafi & & 1.000 & 0.920 & 0.958 & & 0.937 & 0.970 & 0.953 & & 0.993 & 0.991 & 0.992\\
& istibsar & & 1.000 & 0.973 & 0.986 & & 0.977 & 0.950 & 0.963 & & 0.996 & 0.998 & 0.997\\ \cline{2-14}
 & &  & 1.000 & 0.964 & 0.982 & & 0.936 & 0.968 & 0.951 & & 0.995 & 0.996 & 0.995 \\
 \end{tabular}                 
}                             
\normalsize                   
\label{t:nopunctlearnresults} 
\end{table*}
